Global patterns of forest autotrophic carbon fluxes

### 2019-09-12 manuscript/manuscript draft.Rmd
re-wrote Table 1 questions as hypotheses

\renewcommand{\arraystretch}{2}
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "Hypothesis table") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  pack_rows("1. How do FACF vary with latitude?", 1, 3, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("2. How do FACF relate to MAT and MAP?", 4, 6, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("3. How do FACF relate to other annual climate variables?", 7, 9, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("4. What is the role of seasonality?", 10, 13, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("5. Per month of the growing seaon, how do FACF vary with climate?", 14, 17, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  add_header_above(c(" ", " ", " ", "Forest autotrophic carbon fluxes (FACF)" = 9, " ")) %>%
  column_spec(1, width = "10cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3:13, width = "1.8cm") %>%
  kableExtra::landscape()
```

@@

| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Annual gross primary production; annual uptake of carbon dioxide by an ecosystem | NA | Flux partitioning of eddy covariance | 243 | 49 |
| $NPP$ | Annual net primary production; the component of GPP that is stored in plant tissue; GPP minus ecosystem respiration | Foliage, branch, stem, coarse root and fine root | Direct measurement of annual increments of components | 92 | 42 |
| $ANPP$ | Aboveground net primary production | Foliage, stem, and optionally branch | Direct measurement of annual increments of components | 256 | 80 |
| $ANPP_{foliage}$ | Net primary production of foliage | Foliage | Direct measurement of litterfall, correcting for changes in leaf biomass when measured | 98 | 49 |
| $ANPP_{woody-stem}$ | Net primary production of woody stems | Woody stems | Direct measurement of stem growth increment | 264 | 96 |
| $BNPP_{root}$  | Belowground net primary production | Coarse and fine roots | Direct measurement of one or more of: fine root turnover, soil cores, root ingrowth cores, minirhizotrons; indirect estimates of coarse roots using allometries based on aboveground stem increment measures | 101 | 48 |
| $BNPP_{fine.root}$ | Net primary production of fine roots | Fine roots | Direct measurement of one or more of: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 88 | 41 |
| $R_{auto}$ | Annual autotrophic respiration, including above- and belowground components | Foliage, stem, and root | Chamber measurements of component gas exchange | 22 | 13 |
| $R_{root}$ | Annual root respiration | Coarse and fine roots | Measurement of root gas exchange | 64 | 26 |

@@

### Acknowledgements
Scholarly Studies
ForestGEO
Compilatin of the ForC database was originally funded by DOE

>>>>

\renewcommand{\arraystretch}{2}
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "Hypothesis table") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  pack_rows("H1. FACF decreases linearly with latitude.", 1, 3, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("H2. FACF increases with MAT, with an interactive effect of MAP.", 4, 6, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("H3. FACF are strongly correlated with other annual climate variables.", 7, 9, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("H4. FACF is reduced under seasonal climates.", 10, 13, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("H5. Considering only growing season months, FACF correlates with climatic drivers.", 14, 17, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  add_header_above(c(" ", " ", " ", "Forest autotrophic carbon fluxes (FACF)" = 9, " ")) %>%
  column_spec(1, width = "10cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3:13, width = "1.8cm") %>%
  kableExtra::landscape()
```

@@

| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Annual gross primary production; annual uptake of carbon dioxide by an ecosystem | NA | Flux partitioning of eddy covariance | 243 | 49 |
| $NPP$ | Annual net primary production; the component of GPP that is stored in plant tissue; $GPP - R_{auto}$ | Foliage, branch, stem, coarse root and fine root | Direct measurement of annual increments of components | 92 | 42 |
| $ANPP$ | Aboveground net primary production | Foliage, stem, and optionally branch | Direct measurement of annual increments of components | 256 | 80 |
| $ANPP_{foliage}$ | Net primary production of foliage | Foliage | Direct measurement of litterfall, correcting for changes in leaf biomass when measured | 98 | 49 |
| $ANPP_{woody-stem}$ | Net primary production of woody stems | Woody stems | Direct measurement of stem growth increment | 264 | 96 |
| $BNPP_{root}$  | Belowground net primary production | Coarse and fine roots | Direct measurement of one or more of: fine root turnover, soil cores, root ingrowth cores, minirhizotrons; indirect estimates of coarse roots using allometries based on aboveground stem increment measures | 101 | 48 |
| $BNPP_{fine.root}$ | Net primary production of fine roots | Fine roots | Direct measurement of one or more of: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 88 | 41 |
| $R_{auto}$ | Annual autotrophic respiration, including above- and belowground components | Foliage, stem, and root | Chamber measurements of component gas exchange | 22 | 13 |
| $R_{root}$ | Annual root respiration | Coarse and fine roots | *Measurement of root gas exchange, root exclusion from soil respiration chambers* | 64 | 26 |

@@

### Acknowledgements
Scholarly Studies
ForestGEO
Compilation of the ForC database was originally funded by DOE
